---
title: "Yara Air ambient data summary"
author: "Brad Zhang"
date: "`r format(Sys.time(), '%d %B, %Y')`"

draft: "INTERNAL USE ONLY"
output: 
  word_document:
    reference_docx: Data_dictionary_and_data_issues_template.docx
code_folding: hide
---

:::{custom-style="Internal.use.Style"}
INTERNAL USE ONLY
:::



```{r, echo=FALSE, message=FALSE,warning=FALSE}
library(tidyverse);library(pander); library(captioner);library(gtable)
setwd("C:/Users/213002h/OneDrive - Curtin/iDrive/Yara_data")
```
 
```{r, echo=FALSE, message=FALSE,warning=FALSE}
#set pander table-layout options
panderOptions('table.alignment.default', function(df)
    ifelse(sapply(df, is.numeric), 'right', 'left'))
panderOptions('table.split.table', Inf)
panderOptions('big.mark', "")
panderOptions('keep.trailing.zeros', TRUE)
panderOptions("table.emphasize.rownames",FALSE)
panderOptions('keep.line.breaks', TRUE)

# #Set table and figure caption numbering
table_nums <- captioner(prefix = "Table")
```
# Historical and current industrial data
```{r health_passive, echo=FALSE}
Yara_air_ambient <- data.frame(
  Variable_names = c("Site",
                    "Sampler_type",
                    "Lot_number",
                    "Sticker_ID",
                    "Date_Time_on",
                    "Date_Time_off",
                    "Ammonia_as_N_pertube",
                    "Nitrate_as_NO3_pertube",
                    "Nitrite_as_NO2_pertube",
                    "Sulphate_as_SO4_pertube",
                    "NO2_pertube",
                    "HNO3_pertube",
                    "SO2_pertube",
                    "NH3_pertube",
                    "NO2_update_rate",
                    "HNO3_update_rate",
                    "SO2_update_rate", 
                    "NH3_update_rate",
                    "NO2_blank_corrected",
                    "HNO3_blank_corrected",
                    "SO2_blank_corrected",
                    "NH3_blank_corrected",
                    "NO2_temp_corrected",
                    "HNO3_temp_corrected",
                    "SO2_temp_corrected",
                    "NH3_temp_corrected",
                    "NO2",
                    "HNO3",
                    "SO2",
                    "NH3",
                    "Site_n",
                    "longitude",
                    "latitude",
                    "Rock_type",
                    "datefix"),
  Notes = c("Yara air quality sampling sites",
                    "CSIRO or Radiello",
                    "Lot_number only for Radiello",
                    "Sample individual ID",
                    "Time starting the passive sampling",
                    "Time ending the passive sampling",
                    "Ammonia per tube as N",
                    "Nitrate per tube as NO3",
                    "Nitrite per tube as NO2",
                    "Sulphate per tube as SO4",
                    "NO2 per tube reported as gases",
                    "HNO3 per tube reported as gases",
                    "SO2 per tube reported as gases",
                    "NH3 per tube reported as gases",
                    "NO2 Uptake Rate (corrected for temp) (mL/min)",			
                    "HNO3 Uptake Rate (corrected for temp) (mL/min)",
                    "SO2 Uptake Rate (corrected for temp) (mL/min)", 
                    "NH3 Uptake Rate (corrected for temp) (mL/min)",
                    "Blank Corrected",
                    "Blank Corrected",
                    "Blank Corrected",
                    "Blank Corrected",
                    "Temperature Corrected",
                    "Temperature Corrected",
                    "Temperature Corrected",
                    "Temperature Corrected",
                    "NO2 Concentrations (Negative values reported as zero)",
                    "HNO3 Concentrations (Negative values reported as zero)",
                    "SO2 Concentrations (Negative values reported as zero)",
                    "NH3 Concentrations (Negative values reported as zero)",
                    "an individual number for each site",
                    "",
                    "",
                    "Rock type",
                    "a variable fixing the date issue"),
  Units = c(rep("", 6),
            rep("µg/tube (DL used for ND)", 8),
            rep("mL/min", 4),
            rep("µg/tube", 4),
            rep("µg/m3", 8),
            rep("", 5))
)

Yara_air_ambient_cap<-table_nums(name = "Yara_air_ambient.cap", 
                          caption = "Summary table of Yara_air_ambient data")

pander(Yara_air_ambient, style = "multiline", 
      caption = Yara_air_ambient_cap, 
       justify = c('left','left','left'))


```

_________________________________________________________________________________
---
## Notes:
Yara Historical data from  Ambient Air_25_10_2022.xlsx at level 0. Passive sampling methods has been employed. The concentration of NO~2~, SO~2~, NH~3~ and NO~3~ was calculated using the following formula with temperature correction.    

$$Q_K = Q_{298} (\frac{K}{298} )^{7,0}$$


## Issues:
- For sites, the site names were not filled in for each row. We need to use R to fix this.
- Date variables were not in a consistent format.
- Strings for the numerical variables such as concentrations or ug per tube were replaced by "missing". 
- values in italics = nd, DL used, the information cannot be kept in the final csv file.
