---
output:
  html_document: default
  pdf_document: default
---
---
title: "Yara Ambient air data"
author: "Brad Zhang"
date: "`r format(Sys.time(), '%d %B, %Y')`"
draft: "INTERNAL USE ONLY"
:::{custom-style="Internal.use.Style"}


***Part 1-setup***
```{r, message=FALSE,warning=FALSE}
setwd("C:/Users/213002h/OneDrive - Curtin/iDrive/Yara_data")
library(tidyverse)
library(readxl)
```
***Part 2 -read the data and select variables and name the variables***
```{r, message=FALSE, warning=FALSE}
Ambient_Air = read_excel("Ambient Air_25_10_2022.xlsx", sheet = "Radiello Concn Calcs", skip=1)
Ambient_Air2 = cbind(Ambient_Air[,1:10], Ambient_Air[,13:16],Ambient_Air[,22:33], Ambient_Air[,40:43]) 
colnames(Ambient_Air2)[1:10]=c("Site", "Sampler_type", "Lot_number", "Sticker_ID", "Date_Time_on", "Date_Time_off", "Ammonia_as_N_pertube", "Nitrate_as_NO3_pertube", "Nitrite_as_NO2_pertube", "Sulphate_as_SO4_pertube")
colnames(Ambient_Air2)[11:14]=c("NO2_pertube", "HNO3_pertube", "SO2_pertube", "NH3_pertube")
colnames(Ambient_Air2)[15:18]=c("NO2_uptake_rate", "HNO3_uptake_rate", "SO2_uptake_rate", "NH3_uptake_rate")
colnames(Ambient_Air2)[19:22]=c("NO2_blank_corrected", "HNO3_blank_corrected", "SO2_blank_corrected", "NH3_blank_corrected")
colnames(Ambient_Air2)[23:26]=c("NO2_temp_corrected", "HNO3_temp_corrected", "SO2_temp_corrected", "NH3_temp_corrected")
colnames(Ambient_Air2)[27:30]=c("NO2", "HNO3", "SO2", "NH3")
```
**Part 3 -adding site names for "NA"**
  ```{r, message=FALSE,warning=FALSE}
site=Ambient_Air2[[1]]
x=site[1]
for (i in seq_along(site)) {
  if (is.na(site[i])==T) {
    site[i]=x
  }
  else {
    x=site[i]
  }
} 
Ambient_Air2$Site=site
```
***Part 4 -change the variables from Character to numeric with a round 2 and add site ID*** 
```{r, message=FALSE, warning=FALSE}
Ambient_Air2[,7:30] = lapply(Ambient_Air2[,7:30], as.numeric)
Ambient_Air2[,7:30] = lapply(Ambient_Air2[,7:30], round, 2)
Ambient_Air2$Site_n = as.numeric(substr(Ambient_Air2$Site, 6,6))
```
**Part 5 -add the GPS and Rocktype**
```{r}
Ambient_Air2$longitude = ifelse(Ambient_Air2$Site_n==5, 116.769256, ifelse(Ambient_Air2$Site_n==6, 116.7859513, 116.7884007))
Ambient_Air2$latitude = ifelse(Ambient_Air2$Site_n==5, -20.62107548, ifelse(Ambient_Air2$Site_n==6, -20.61778979, -20.63722019))
Ambient_Air2$Rock_type= ifelse(Ambient_Air2$Site_n<7, "Granophyre", "Gabbro")
```
**Part 6 -Fix the date issue**
```{r, message=FALSE, warning=FALSE}
Ambient_Air2$datefix = ifelse(as.numeric(substr(Ambient_Air2$Date_Time_on, 1,2))==43, 1,2)
Ambient_Air2$date_on_number = ifelse(Ambient_Air2$datefix==1, as.numeric(Ambient_Air2$Date_Time_on), 0)  
Ambient_Air2$date_on_date = as.Date(Ambient_Air2$date_on_number, origin = "1899-12-30")    
Ambient_Air2$Date_Time_on = ifelse(Ambient_Air2$datefix==1, as.character(Ambient_Air2$date_on_date), Ambient_Air2$Date_Time_on)
Ambient_Air2$date_off_number = ifelse(Ambient_Air2$datefix==1, as.numeric(Ambient_Air2$Date_Time_off), 0)  
Ambient_Air2$date_off_date = as.Date(Ambient_Air2$date_off_number, origin = "1899-12-30")    
Ambient_Air2$Date_Time_off = ifelse(Ambient_Air2$datefix==1, as.character(Ambient_Air2$date_off_date), Ambient_Air2$Date_Time_off)

Ambient_Air2 <- subset(Ambient_Air2, select = -c(date_on_number, date_on_date, date_off_number, date_off_date))
```
**Part 7 -save the data as Ambient Ambient_Air.csv**
```{r}
write.csv(Ambient_Air2, "Ambient_Air_22_11_2022.csv")
```
### Session Info
```{r}
sessionInfo()
```


